|

### 2016-05-25 Benchmark/MSGF-Benchmark/msgf-benchmark.Rmd
benchmark

p3_table <- fData(msexp_p3)
ns_table <- fData(msexp_no_switch)
```

@@

```{r, echo = F, include=F}
library(mzID)
evalue = 1e-10
pnnl <- mzid_pnnl[, c("Scan", "MSGFDB_SpecEValue", "Peptide")]
p3_flt <- flatten(mzid_p3)
bigmzid <- merge(pnnl, p3_table[, c("scan number(s)", "ms-gf:specevalue", "pepseq")], by.x="Scan", by.y = "scan number(s)", all.x = T, all.y = T)
```

@@

# 6. Filtering
```{r, include=F}
pnnl$Peptide <- substr(as.character(pnnl$Peptide),1,nchar(as.character(pnnl$Peptide))-2)
pnnl$Peptide <- substr(as.character(pnnl$Peptide),3,nchar(as.character(pnnl$Peptide)))
```

@@

bt_tmp <- merge(x =  tmp, y=pnnl, by.y = "Scan", by.x  =  "scan number(s)", all.x = T)
bt_tmp <- bt_tmp[order(bt_tmp$`ms-gf:specevalue`, decreasing = F),]
```
There are ```r nrow(tmp)``` rows remained.

### Differences
Data from Docker is matched with from PNNL using scan number as ID. `r names(bt_tmp)[2:4]` are values from Docker, `r names(bt_tmp)[5:7]` are the corresponding values from PNNL. There are `r nrow(bt_tmp)` of rows in total with  `r sum(is.na(bt_tmp$MSGFDB_SpecEValue))` of NULL/unmapped values.

```{r, echo=F}
tmp_nona <- tmp[!is.na(tmp),]
```

Aside from the `r sum(is.na(bt_tmp$MSGFDB_SpecEValue))` unmatched values, `r sum(tmp_nona$'ms-gf:specevalue'!=tmp_nona$MSGFDB_SpecEValue)` unmacthed spec-evalue, `r sum(tmp_nona$pepseq!=tmp_nona$Peptide)` of unmatched peptide identification.

```{r echo=F}
print("==Head==")
head(bt_tmp,2)
print("==Unmatched==")
head(bt_tmp[is.na(bt_tmp$MSGFDB_SpecEValue),],3)
print("==Tail==")
tail(bt_tmp,2)
```

@@

bt_tmp <- merge(x =  tmp, y=pnnl, by.y = "Scan", by.x  =  "scan number(s)", all.x = T)
bt_tmp <- bt_tmp[order(bt_tmp$`ms-gf:specevalue`, decreasing = F),]
```
There are ```r nrow(tmp)``` rows remained.

### Differences:
Data from Docker is matched with from PNNL using scan number as ID. `r names(bt_tmp)[2:4]` are values from Docker, `r names(bt_tmp)[5:7]` are the corresponding values from PNNL. There are `r nrow(bt_tmp)` of rows in total with  `r sum(is.na(bt_tmp$MSGFDB_SpecEValue))` of NULL/unmapped values.
```{r, include=F}
tmp_nona <- tmp[!is.na(tmp),]
```
Aside from the `r sum(is.na(bt_tmp$MSGFDB_SpecEValue))` unmatched values, ```r sum(tmp_nona$'ms-gf:specevalue'!=tmp_nona$MSGFDB_SpecEValue)``` unmacthed spec-evalue, ```r sum(tmp_nona$pepseq!=tmp_nona$Peptide)``` of unmatched peptide identification.

```{r echo=F}
print("==Head==")
head(bt_tmp,2)
print("==Unmatched==")
head(bt_tmp[is.na(bt_tmp$MSGFDB_SpecEValue),],3)
print("==Tail==")
tail(bt_tmp,2)
```

@@

bt_tmp <- merge(x =  tmp, y=pnnl, by.y = "Scan", by.x  =  "scan number(s)", all.x = T)
bt_tmp <- bt_tmp[order(bt_tmp$`ms-gf:specevalue`, decreasing = F),]
```
There are ```r nrow(tmp)``` rows remained.

### Differences
Data from Docker is matched with from PNNL using scan number as ID. `r names(bt_tmp)[2:4]` are values from Docker, `r names(bt_tmp)[5:7]` are the corresponding values from PNNL. There are `r nrow(bt_tmp)` of rows in total with  `r sum(is.na(bt_tmp$MSGFDB_SpecEValue))` of NULL/unmapped values.
```{r, include=F}
tmp_nona <- tmp[!is.na(tmp),]
```
Aside from the `r sum(is.na(bt_tmp$MSGFDB_SpecEValue))` unmatched values, ```r sum(tmp_nona$'ms-gf:specevalue'!=tmp_nona$MSGFDB_SpecEValue)``` unmacthed spec-evalue, ```r sum(tmp_nona$pepseq!=tmp_nona$Peptide)``` of unmatched peptide identification.

```{r echo=F}
print("==Head==")
head(bt_tmp,2)
print("==Unmatched==")
head(bt_tmp[is.na(bt_tmp$MSGFDB_SpecEValue),],3)
print("==Tail==")
tail(bt_tmp,2)
```

# 7. Filtering
```{r, include=F}
pnnl$Peptide <- substr(as.character(pnnl$Peptide),1,nchar(as.character(pnnl$Peptide))-2)
pnnl$Peptide <- substr(as.character(pnnl$Peptide),3,nchar(as.character(pnnl$Peptide)))
```

@@

bt_tmp <- merge(y =  tmp, x=pnnl, by.x = "Scan", by.y  =  "scan number(s)", all.x = T)
bt_tmp <- bt_tmp[order(bt_tmp$`ms-gf:specevalue`, decreasing = F),]
```
There are ```r nrow(tmp)``` rows remained.

### Differences
Data from Docker is matched with from PNNL using scan number as ID. `r names(bt_tmp)[2:4]` are values from Docker, `r names(bt_tmp)[5:7]` are the corresponding values from PNNL. There are `r nrow(bt_tmp)` of rows in total with  `r sum(is.na(bt_tmp$'ms-gf:specevalue'))` of NULL/unmapped values.

```{r, echo=F}
tmp_nona <- tmp[!is.na(tmp),]
```

Aside from the `r sum(is.na(bt_tmp$'ms-gf:specevalue'))` unmatched values, `r sum(tmp_nona$'ms-gf:specevalue'!=tmp_nona$MSGFDB_SpecEValue)` unmacthed spec-evalue, `r sum(tmp_nona$pepseq!=tmp_nona$Peptide)` of unmatched peptide identification.

```{r echo=F}
print("==Head==")
head(bt_tmp,2)
print("==Unmatched==")
head(bt_tmp[is.na(bt_tmp$'ms-gf:specevalue'),],3)
print("==Tail==")
tail(bt_tmp,2)
```

>>>>

p3_table <- fData(msexp_p3)
ns_table <- fData(msexp_no_switch)

pnnl <- mzid_pnnl[, c("Scan", "MSGFDB_SpecEValue", "Peptide")]
pnnl <- pnnl[!duplicated(pnnl$Scan),]
p3_flt <- flatten(mzid_p3)
bigmzid <- merge(pnnl, p3_table[, c("scan number(s)", "ms-gf:specevalue", "pepseq")], by.x="Scan", by.y = "scan number(s)", all.x = T, all.y = T)
pnnl$Peptide <- substr(as.character(pnnl$Peptide),1,nchar(as.character(pnnl$Peptide))-2)
pnnl$Peptide <- substr(as.character(pnnl$Peptide),3,nchar(as.character(pnnl$Peptide)))

@@

```{r, echo = F, include=F}
evalue = 1e-10
```

@@

# 6. Filtering (Docker --> PNNL)

```{r include=F}
evalue = 1e-10
```

@@

bt_tmp <- merge(x =  tmp, y=pnnl, by.y = "Scan", by.x  =  "scan number(s)", all.x = T)
bt_tmp <- bt_tmp[order(bt_tmp$`ms-gf:specevalue`, decreasing = F),]
tmp_nona <- bt_tmp[is.na(bt_tmp$MSGFDB_SpecEValue),]
tmp_nona <- tmp_nona[order(tmp_nona$'ms-gf:specevalue', decreasing = F),]
bt_tmp <- bt_tmp[!is.na(bt_tmp$Peptide),]
```
There are ```r nrow(tmp)``` rows remained.

### Differences
Data from Docker is matched with from PNNL using scan number as ID. `r names(bt_tmp)[2:3]` are values from Docker. `r names(bt_tmp)[4:5]` are the corresponding values from PNNL. There are `r nrow(bt_tmp)` of rows in total with  `r nrow(bt_tmp[((bt_tmp$'ms-gf:specevalue'==bt_tmp$MSGFDB_SpecEValue) & (bt_tmp$pepseq==bt_tmp$Peptide)),])` exact match.

Aside from the `r nrow(tmp_nona)` unmatched values, `r sum(bt_tmp$'ms-gf:specevalue'!=bt_tmp$MSGFDB_SpecEValue)` have different spec-evalue, `r sum(bt_tmp$pepseq!=bt_tmp$Peptide)` of different peptide identification.

```{r echo=F}
print("==Head==")
head(bt_tmp,2)
print("==Tail==")
tail(bt_tmp,2)

print("==Unmatched==")
head(tmp_nona,2)
print("==Different Spec Values==")
head(bt_tmp[(bt_tmp$'ms-gf:specevalue'!=bt_tmp$MSGFDB_SpecEValue),],2)
print("==Different Peptides identification==")
head(bt_tmp[(bt_tmp$pepseq!=bt_tmp$Peptide),],2)

@@

bt_tmp <- merge(x =  tmp, y=pnnl, by.y = "Scan", by.x  =  "scan number(s)", all.x = T)
bt_tmp <- bt_tmp[order(bt_tmp$`ms-gf:specevalue`, decreasing = F),]
tmp_nona <- bt_tmp[is.na(bt_tmp$MSGFDB_SpecEValue),]
tmp_nona <- tmp_nona[order(tmp_nona$'ms-gf:specevalue', decreasing = F),]
bt_tmp <- bt_tmp[!is.na(bt_tmp$Peptide),]
```
There are ```r nrow(tmp)``` rows remained.

### Differences
Data from Docker is matched with from PNNL using scan number as ID. `r names(bt_tmp)[2:3]` are values from Docker. `r names(bt_tmp)[4:5]` are the corresponding values from PNNL. There are `r nrow(bt_tmp)` of rows in total with  `r nrow(bt_tmp[((bt_tmp$'ms-gf:specevalue'==bt_tmp$MSGFDB_SpecEValue) & (bt_tmp$pepseq==bt_tmp$Peptide)),])` exact match.

Aside from the `r nrow(tmp_nona)` unmatched values, `r sum(bt_tmp$'ms-gf:specevalue'!=bt_tmp$MSGFDB_SpecEValue)` have different spec-evalue, `r sum(bt_tmp$pepseq!=bt_tmp$Peptide)` of different peptide identification.

```{r echo=F}
print("==Head==")
head(bt_tmp,2)
print("==Tail==")
tail(bt_tmp,2)

print("==Unmatched==")
head(tmp_nona,2)
print("==Different Spec Values==")
head(bt_tmp[(bt_tmp$'ms-gf:specevalue'!=bt_tmp$MSGFDB_SpecEValue),],2)
print("==Different Peptides identification==")
head(bt_tmp[(bt_tmp$pepseq!=bt_tmp$Peptide),],2)

@@

bt_tmp <- merge(x =  tmp, y=pnnl, by.y = "Scan", by.x  =  "scan number(s)", all.x = T)
bt_tmp <- bt_tmp[order(bt_tmp$`ms-gf:specevalue`, decreasing = F),]
tmp_nona <- bt_tmp[is.na(bt_tmp$MSGFDB_SpecEValue),]
tmp_nona <- tmp_nona[order(tmp_nona$'ms-gf:specevalue', decreasing = F),]
bt_tmp <- bt_tmp[!is.na(bt_tmp$Peptide),]
```
There are ```r nrow(tmp)``` rows remained.

### Differences
Data from Docker is matched with from PNNL using scan number as ID. `r names(bt_tmp)[2:3]` are values from Docker. `r names(bt_tmp)[4:5]` are the corresponding values from PNNL. There are `r nrow(bt_tmp)` of rows in total with  `r nrow(bt_tmp[((bt_tmp$'ms-gf:specevalue'==bt_tmp$MSGFDB_SpecEValue) & (bt_tmp$pepseq==bt_tmp$Peptide)),])` exact match.

Aside from the `r nrow(tmp_nona)` unmatched values, `r sum(bt_tmp$'ms-gf:specevalue'!=bt_tmp$MSGFDB_SpecEValue)` have different spec-evalue, `r sum(bt_tmp$pepseq!=bt_tmp$Peptide)` of different peptide identification.

```{r echo=F}
print("==Head==")
head(bt_tmp,2)
print("==Tail==")
tail(bt_tmp,2)

print("==Unmatched==")
head(tmp_nona,2)
print("==Different Spec Values==")
head(bt_tmp[(bt_tmp$'ms-gf:specevalue'!=bt_tmp$MSGFDB_SpecEValue),],2)
print("==Different Peptides identification==")
head(bt_tmp[(bt_tmp$pepseq!=bt_tmp$Peptide),],2)

# 7. Filtering (PNNL -> Docker)

```{r include=F}
evalue = 1e-10
```

# a. Spec-Evalue `r evalue`
### From PNNL
```{r, echo =F}
pnnl_tmp <- pnnl[pnnl$MSGFDB_SpecEValue<evalue,]
print("==Head==")
head(pnnl_tmp,2)
print("==Tail==")
tail(pnnl_tmp,2)
```
There are ```r nrow(pnnl_tmp)``` rows remained.

@@

bt_tmp <- merge.data.frame(y =  p3_table[,c("scan number(s)", "ms-gf:specevalue", "pepseq")], x=pnnl_tmp, by.x = "Scan", by.y  =  "scan number(s)", all.x = T, all.y = F)
bt_tmp <- bt_tmp[order(bt_tmp$`ms-gf:specevalue`, decreasing = F),]
tmp_nona <- bt_tmp[is.na(bt_tmp$'ms-gf:specevalue'),]
tmp_nona <- tmp_nona[order(tmp_nona$MSGFDB_SpecEValue, decreasing = F),]
bt_tmp <- bt_tmp[!is.na(bt_tmp$'pepseq'),]
```
There are ```r nrow(tmp)``` rows remained.

### Differences
Data from Docker is matched with from PNNL using scan number as ID. `r names(bt_tmp)[2:3]` are values from PNNL. `r names(bt_tmp)[4:5]` are the corresponding values from Docker Container. There are `r nrow(bt_tmp)` of rows in total with   `r nrow(bt_tmp[((bt_tmp$'ms-gf:specevalue'==bt_tmp$MSGFDB_SpecEValue) & (bt_tmp$pepseq==bt_tmp$Peptide)),])` exact match.

Aside from the `r nrow(tmp_nona)` unmatched values, `r sum(bt_tmp$'ms-gf:specevalue'!=bt_tmp$MSGFDB_SpecEValue)` have different spec-evalue, `r sum(bt_tmp$pepseq!=bt_tmp$Peptide)` of different peptide identification.

```{r echo=F}
print("==Head==")
head(bt_tmp,2)
print("==Unmatched==")
head(tmp_nona,3)
print("==Tail==")
tail(bt_tmp,2)

print("==Unmatched==")
head(tmp_nona,2)
print("==Different Spec Values==")
head(bt_tmp[(bt_tmp$'ms-gf:specevalue'!=bt_tmp$MSGFDB_SpecEValue),],2)
print("==Different Peptides identification==")
head(bt_tmp[(bt_tmp$pepseq!=bt_tmp$Peptide),],2)

# b. Spec-Evalue `r evalue`

### From PNNL
```{r, echo =F}
pnnl_tmp <- pnnl[pnnl$MSGFDB_SpecEValue<evalue,]
head(pnnl_tmp,2)
tail(pnnl_tmp,2)
```
There are ```r nrow(pnnl_tmp)``` rows remained.

bt_tmp <- merge.data.frame(y =  p3_table[,c("scan number(s)", "ms-gf:specevalue", "pepseq")], x=pnnl_tmp, by.x = "Scan", by.y  =  "scan number(s)", all.x = T, all.y = F)
bt_tmp <- bt_tmp[order(bt_tmp$`ms-gf:specevalue`, decreasing = F),]
tmp_nona <- bt_tmp[is.na(bt_tmp$'ms-gf:specevalue'),]
tmp_nona <- tmp_nona[order(tmp_nona$MSGFDB_SpecEValue, decreasing = F),]
bt_tmp <- bt_tmp[!is.na(bt_tmp$'pepseq'),]
```
There are ```r nrow(tmp)``` rows remained.

### Differences
Data from Docker is matched with from PNNL using scan number as ID. `r names(bt_tmp)[2:3]` are values from PNNL. `r names(bt_tmp)[4:5]` are the corresponding values from Docker Container. There are `r nrow(bt_tmp)` of rows in total with   `r nrow(bt_tmp[((bt_tmp$'ms-gf:specevalue'==bt_tmp$MSGFDB_SpecEValue) & (bt_tmp$pepseq==bt_tmp$Peptide)),])` exact match.

Aside from the `r nrow(tmp_nona)` unmatched values, `r sum(bt_tmp$'ms-gf:specevalue'!=bt_tmp$MSGFDB_SpecEValue)` have different spec-evalue, `r sum(bt_tmp$pepseq!=bt_tmp$Peptide)` of different peptide identification.

```{r echo=F}
print("==Head==")
head(bt_tmp,2)
print("==Unmatched==")
head(tmp_nona,3)
print("==Tail==")
tail(bt_tmp,2)

print("==Unmatched==")
head(tmp_nona,2)
print("==Different Spec Values==")
head(bt_tmp[(bt_tmp$'ms-gf:specevalue'!=bt_tmp$MSGFDB_SpecEValue),],2)
print("==Different Peptides identification==")
head(bt_tmp[(bt_tmp$pepseq!=bt_tmp$Peptide),],2)

# c. Spec-Evalue `r evalue`

### From PNNL
```{r, echo =F}
pnnl_tmp <- pnnl[pnnl$MSGFDB_SpecEValue<evalue,]
head(pnnl_tmp,2)
tail(pnnl_tmp,2)
```
There are ```r nrow(pnnl_tmp)``` rows remained.

bt_tmp <- merge.data.frame(y =  p3_table[,c("scan number(s)", "ms-gf:specevalue", "pepseq")], x=pnnl_tmp, by.x = "Scan", by.y  =  "scan number(s)", all.x = T, all.y = F)
bt_tmp <- bt_tmp[order(bt_tmp$`ms-gf:specevalue`, decreasing = F),]
tmp_nona <- bt_tmp[is.na(bt_tmp$'ms-gf:specevalue'),]
tmp_nona <- tmp_nona[order(tmp_nona$MSGFDB_SpecEValue, decreasing = F),]
bt_tmp <- bt_tmp[!is.na(bt_tmp$'pepseq'),]
```
There are ```r nrow(tmp)``` rows remained.

### Differences
Data from Docker is matched with from PNNL using scan number as ID. `r names(bt_tmp)[2:3]` are values from PNNL. `r names(bt_tmp)[4:5]` are the corresponding values from Docker Container. There are `r nrow(bt_tmp)` of rows in total with   `r nrow(bt_tmp[((bt_tmp$'ms-gf:specevalue'==bt_tmp$MSGFDB_SpecEValue) & (bt_tmp$pepseq==bt_tmp$Peptide)),])` exact match.

Aside from the `r nrow(tmp_nona)` unmatched values, `r sum(bt_tmp$'ms-gf:specevalue'!=bt_tmp$MSGFDB_SpecEValue)` have different spec-evalue, `r sum(bt_tmp$pepseq!=bt_tmp$Peptide)` of different peptide identification.

```{r echo=F}
print("==Head==")
head(bt_tmp,2)
print("==Unmatched==")
head(tmp_nona,3)
print("==Tail==")
tail(bt_tmp,2)

print("==Unmatched==")
head(tmp_nona,2)
print("==Different Spec Values==")
head(bt_tmp[(bt_tmp$'ms-gf:specevalue'!=bt_tmp$MSGFDB_SpecEValue),],2)
print("==Different Peptides identification==")
head(bt_tmp[(bt_tmp$pepseq!=bt_tmp$Peptide),],2)
